
Dear [SIR/MADAM],
\doublenewline
Good day. \\
I hope that you're doing well!
\doublenewline
I am writing to express my interest in the position, [POSITION], listed in [GAIJINPOT OR SOMETHING]. 
I am a native-speaker of English from the Philippines, with a diverse background in several fields, including enthusiastically teaching elementary school students, Japanese studies, and software engineering. 
\doublenewline
I am currently based in Kanagawa-ken, holding a visa in the following category, "Engineer/Specialist in Humanities/Int'l Services", and seek an exciting and challenging position at your institution. I hold a bachelor's degree in Computer Science from the University of the Philippines, and a diploma in Japanese Studies in Meiji Gakuin University. I have recently scored an 8.0 in the International English Language Testing System, or IELTS. Thus, I am confident that I can more than satisfy the requirements listed for the position.
\doublenewline
Thank you very much for your time and consideration. I am very eager to meet with you to discuss this position, as I believe that I would be an asset to the institution's team of educators, and would enjoy working at [INSTITUTION NAME]. I am available to further discuss my qualifications and availability at your convenience and can be most easily contacted by mobile phone at 080-4921-1306, or by Skype, kiefer.yap. I look forward to hearing from you.
\doublenewline
Thank you very much.
\doublenewline
Best Regards,
\\
Jon Kiefer Yap